3D seismic diffraction separation and imaging using the local rank-reduction method

### 2022-01-03 diffrlrra3d/paper.tex
Mon Jan  3 09:21:50 CST 2022

%uncomment
%\inputdir{plot}
%\multiplot{2}{ovp,o}{width=0.6\columnwidth}{(a) Velocity model of the first synthetic example. (b) Zero-offset data simulated from the velocity model.}
%
%\multiplot{6}{o-pwd,o-lrr,o-lrra,o-pwd-n-0,o-lrr-n-0,o-lrra-n-0}{width=0.3\columnwidth}{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. Second row: separated diffractions using (d) the PWD method, (e) the LRR method, and (f) the LRRA method.}
%
%\multiplot{3}{o-pwd-imag-0,o-lrr-imag-0,o-lrra-imag-0}{width=0.45\columnwidth}{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. The arrows indicate less reflection energy and higher resolution using the LRRA method.}

%\multiplot{2}{kvp,k}{width=0.6\columnwidth}{(a) Velocity model of the second synthetic example. (b) Zero-offset data simulated from the velocity model.}
%
%\multiplot{6}{k-pwd,k-lrr,k-lrra,k-pwd-n-0,k-lrr-n-0,k-lrra-n-0}{width=0.3\columnwidth}{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. Second row: separated diffractions using (d) the PWD method, (e) the LRR method, and (f) the LRRA method.}
%
%\multiplot{3}{k-pwd-imag-0,k-lrr-imag-0,k-lrra-imag-0}{width=0.45\columnwidth}{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }
%

>>>>

%uncomment
\inputdir{o}
\multiplot{2}{ovp,o}{width=0.6\columnwidth}{(a) Velocity model of the first synthetic example. (b) Zero-offset data simulated from the velocity model.}

\multiplot{6}{o-pwd,o-lrr,o-lrra,o-pwd-n-0,o-lrr-n-0,o-lrra-n-0}{width=0.3\columnwidth}{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. Second row: separated diffractions using (d) the PWD method, (e) the LRR method, and (f) the LRRA method.}

\multiplot{3}{o-pwd-imag-0,o-lrr-imag-0,o-lrra-imag-0}{width=0.45\columnwidth}{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. The arrows indicate less reflection energy and higher resolution using the LRRA method.}

\inputdir{k}
\multiplot{2}{kvp,k}{width=0.6\columnwidth}{(a) Velocity model of the second synthetic example. (b) Zero-offset data simulated from the velocity model.}

\multiplot{6}{k-pwd,k-lrr,k-lrra,k-pwd-n-0,k-lrr-n-0,k-lrra-n-0}{width=0.3\columnwidth}{First row: separated reflection data using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. Second row: separated diffractions using (d) the PWD method, (e) the LRR method, and (f) the LRRA method.}

\multiplot{3}{k-pwd-imag-0,k-lrr-imag-0,k-lrra-imag-0}{width=0.45\columnwidth}{Migrated diffraction image using (a) the PWD method, (b) the LRR method, and (c) the LRRA method. }
